Simulating NHST and TOST

### 2017-10-14 NHST_and_TOST.Rmd
add html

---
title: "Simulating NHST and TOST"
output:
  pdf_document: default
  html_notebook: default
  html_document: default
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Simulating NHST and TOST"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---
